Managing Relationships\\between Code and Documentation

### 2013-03-21 P6-15-min-talk/talk.tex
submited version

\section{Problem Statement}
\subsection{Problems}
\begin{frame}[b]{\centerline{Problem}}
  \ \\
  \fontsize{13.5}{11}\selectfont How to represent the code segments with
  \begin{itemize}
  \item code-evolving invariance,
  \item good granularity,
  \item and non-ambiguity? %\normalsize
  \end{itemize}
  \begin{center}
  \includegraphics[width=.9\textwidth]{problem3}
  \end{center}
\end{frame}
%\note[enumerate]       % Add notes to yourself that will be displayed when
%{                      % typeset with the notes or notesonly class options
%\item Note for Point 1   
%\item Note for Point 2   
%}

\section{Previous Solution}
\subsection{Previous Solutions}
\begin{frame}{\centerline{Previous Solutions}}
  \ \\
  \fontsize{13.5}{11}\selectfont Previous work addresses this problem by
  \begin{itemize}
  \item comment-based representation
  \item and offset-based representation.
  \end{itemize}
\end{frame}

\subsection{Comment-Representation}
\begin{frame}
  \frametitle{\centerline{Comment-Based Representation (CBR)}}
  \fontsize{13.5}{11}\selectfont
  \begin{columns}[c]
  \column{2.5in}  % slides are 3in high by 5in wide
  advantage: 
  \begin{itemize}
  \item code-evolving invariance
  \end{itemize}
  \vspace{2em}
  disadvantage: 
  \begin{itemize}
  \item bad granularity
  \item ambiguity
  \end{itemize}
  \column{1.5in}
  \includegraphics[height=.9\textheight]{comment}
  \end{columns}
\end{frame}

\subsection{Offset-Representation}
\begin{frame}
  \frametitle{\centerline{Offset-Based Representation (OBR)}}
  \fontsize{13.5}{11}\selectfont
  \begin{columns}[c]
  \column{2in}  % slides are 3in high by 5in wide
  advantage: 
  \begin{itemize}
  \item good granularity
  \item no ambiguity
  \end{itemize}
  \vspace{2em}
  disadvantage: 
  \begin{itemize}
  \item stop working when code evolves
  \end{itemize}
  \column{2in}
  \includegraphics[height=.9\textheight]{offset}
  \end{columns}
\end{frame}

@@

\subsection{Code-evolving Invariance}
\begin{frame}
  \frametitle{\centerline{AST-Based Representation (ABR)}}
  \begin{columns}[c]
  \column{1.8in}  % slides are 3in high by 5in wide
  \includegraphics[width=.9\textwidth]{code11}
  \column{2.5in}
  \includegraphics[height=.75\textheight]{ast11}
  \end{columns}
\end{frame}

@@

\section{Preliminary Result}
\subsection{Preliminary Result}
\begin{frame}{\centerline{Preliminary Result}}
  \ \\
  \begin{center}
  \includegraphics[width=\textwidth]{platformview}
  \end{center}
\end{frame}

\subsection{Preliminary Result}
\begin{frame}[b]{\centerline{Preliminary Result}}
  \fontsize{13.5}{11}\selectfont
  \begin{itemize}
  \item preserve all the relationships for this test case
  \item provide good granularity
  \end{itemize}
  \centerline{\includegraphics[width=.9\textwidth]{platformview}}
\end{frame}

\section{Conclusion}
\begin{frame}[t]{\centerline{Conclusion}}
  \ \\
  \fontsize{13.5}{11}\selectfont
  \centerline{
  \begin{tabular}{*{4}{c}}
    \toprule
    Strategy & Invariance & Granularity & Non-Ambiguity \\
    \midrule
    CBR   & Yes & No  & No \\
    OBR   & No  & Yes & Yes \\
    ABR   & Yes & Yes & Yes \\
    \bottomrule
  \end{tabular}
  }
\end{frame}

\section{Question}
\begin{frame}[t]{\centerline{Conclusion}}
  \ \\
  \fontsize{13.5}{11}\selectfont
  \centerline{
  \begin{tabular}{*{4}{c}}
    \toprule
    Strategy & Invariance & Granularity & Non-Ambiguity \\
    \midrule
    CBR   & Yes & No  & No \\
    OBR   & No  & Yes & Yes \\
    ABR   & Yes & Yes & Yes \\
    \bottomrule
  \end{tabular}
  }
  \begin{center}
  \begin{Huge}
  \ \\
  \ \\
  Question?
  \end{Huge}
  \end{center}
\end{frame}

>>>>

\section{Problem Statement}
\subsection{Problems}
\begin{frame}[b]{\centerline{Problem}}
  \ \\
  \fontsize{13.5}{11}\selectfont How to represent the code segments with
  \begin{itemize}
  \item code-evolving invariance,
  \item flexible granularity,
  \item and non-ambiguity? %\normalsize
  \end{itemize}
  \begin{center}
  \includegraphics[width=.9\textwidth]{problem3}
  \end{center}
\end{frame}
%\note[enumerate]       % Add notes to yourself that will be displayed when
%{                      % typeset with the notes or notesonly class options
%\item Note for Point 1   
%\item Note for Point 2   
%}

\section{Previous Solution}
\subsection{Previous Solutions}
\begin{frame}{\centerline{Previous Work}}
  \ \\
  \fontsize{13.5}{11}\selectfont
  \begin{itemize}
  \item Comment-based representation
    \begin{itemize}
      \item Javadoc uses this to write documentation for code segments.
    \end{itemize}
  \ \\
  \ \\
  \item Offset-based representation
    \begin{itemize}
      \item Compiler uses this method to highlight error code.
    \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Comment-Representation}
\begin{frame}
  \frametitle{\centerline{Comment-Based Representation}}
  \fontsize{13.5}{11}\selectfont
  \begin{columns}[c]
  \column{2.5in}  % slides are 3in high by 5in wide
  Advantage
  \begin{itemize}
  \item Code-evolving invariance
  \end{itemize}
  \vspace{2em}
  Disadvantage
  \begin{itemize}
  \item Coarse granularity
  \item Ambiguity
  \end{itemize}
  \column{1.5in}
  \includegraphics[height=.9\textheight]{comment}
  \end{columns}
\end{frame}

\subsection{Offset-Representation}
\begin{frame}
  \frametitle{\centerline{Offset-Based Representation}}
  \fontsize{13.5}{11}\selectfont
  \begin{columns}[c]
  \column{2in}  % slides are 3in high by 5in wide
  Advantage
  \begin{itemize}
  \item Flexible granularity
  \item No ambiguity
  \end{itemize}
  \vspace{2em}
  Disadvantage
  \begin{itemize}
  \item No code-evolving invariance
  \end{itemize}
  \column{2in}
  \includegraphics[height=.9\textheight]{offset}
  \end{columns}
\end{frame}

@@

\subsection{Code-evolving Invariance}
\begin{frame}
  \frametitle{\centerline{AST-Based Representation}}
  \begin{columns}[c]
  \column{1.8in}  % slides are 3in high by 5in wide
  \includegraphics[width=.9\textwidth]{code11}
  \column{2.5in}
  \includegraphics[height=.75\textheight]{ast11}
  \end{columns}
\end{frame}

@@

\section{Preliminary Result}
\subsection{Preliminary Result}
\begin{frame}{\centerline{Preliminary Result}}
  \begin{center}
  \includegraphics[width=.9\textwidth]{platformview}
  \end{center}
\end{frame}

\subsection{Preliminary Result}
\begin{frame}[b]{\centerline{Preliminary Result}}
  \fontsize{13.5}{11}\selectfont
  \begin{itemize}
  \item Preserve all the relationships after code evolves.
  \item Provide flexible granularity and non-ambiguity.
  \end{itemize}
  \centerline{\includegraphics[width=.7\textwidth]{platformview}}
\end{frame}

\section{Conclusion}
\begin{frame}[t]{\centerline{Conclusion}}
  \ \\
  \fontsize{10}{11}\selectfont
  \centerline{
  \begin{tabular}{rccc}
    \toprule
    Representation & Code-evolving invariance & Flexible granularity & Non-ambiguity \\
    \midrule
    Comment based   & Yes & No  & No \\
    Offset based   & No  & Yes & Yes \\
    AST based   & Yes & Yes & Yes \\
    \bottomrule
  \end{tabular}
  }
\end{frame}

\section{Question}
\begin{frame}[t]{\centerline{Conclusion}}
  \ \\
  \fontsize{10}{11}\selectfont
  \centerline{
  \begin{tabular}{rccc}
    \toprule
    Representation & Code-evolving invariance & Flexible granularity & Non-ambiguity \\
    \midrule
    Comment based   & Yes & No  & No \\
    Offset based   & No  & Yes & Yes \\
    AST based   & Yes & Yes & Yes \\
    \bottomrule
  \end{tabular}
  }
  \begin{center}
  \begin{Huge}
  \ \\
  \ \\
  Question?
  \end{Huge}
  \end{center}
\end{frame}
